Toxic code snippets on Stack Overflow

### 2017-10-20 cloverflow-tse/cloverflow.tex
Small changes to FIXMEs and adding one more related work by Abdalkareem et al.

\subsection{Stack Overflow Developers' Survey} We support our findings of
toxic code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and license-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our research note~
\FIXME{add URL to the RN}.

@@

We received 201 answers (33\% response rate) from 607 emails we sent to the
Stack Overflow answerers. The response rate was high
considered other online survey in software engineering that received
approximately 14--20\%~\FIXME{double-check the citation again for the magic
	numbers.}\cite{Punter2003}.
We only present a summary of the survey answers in
this paper and the full analysis is available as a technical report \FIXME{add URL}.

@@

The work that is closely similar to us is a study by 
An et al.~\cite{An2017} where the authors investigated 
clones between 399 Android apps and Stack Overflow posts. 
They found 1,226 code snippets which were reused from 68 Android apps. 
They also observed that there are 1,279 cases of potential 
license violations. The authors rely on the timestamp to 
judge whether the code has been copied from/to Stack Overflow 
along with confirmations from six developers. Instead of Android apps, 
we investigated clones between Stack Overflow and 111 open 
source projects. Their results are similar to our findings that 
there exist clones from software projects to Stack Overflow with 
potential licensing violations. 
\FIXME{Add a discussion of Abdalkareem et al.~\cite{Abdalkareem2017}}
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.

>>>>

\subsection{Stack Overflow Developers' Survey} We support our findings of
toxic code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and license-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our research note~
\cite{Ragkhitwetsagul_RN2017}~\FIXME{Fix the RN bibtex}.

@@

We received 201 answers (33\% response rate) from 607 emails we sent to the
Stack Overflow answerers. The response rate was high
considered other online survey in software engineering that received
approximately 14--20\%~\FIXME{double-check the citation again for the magic
	numbers.}\cite{Punter2003}.
We only present a summary of the survey answers in
this paper and the full analysis is available as a technical report~\cite{Ragkhitwetsagul_RN2017}.

@@

The work that are closely similar to us are studies by An et al.~\cite{An2017}
and Abdalkareem et al.~\cite{Abdalkareem2017}. An et al.~investigated clones
between 399 Android apps and Stack Overflow posts. They found 1,226 code
snippets which were reused from 68 Android apps. They also observed that there
are 1,279 cases of potential license violations. The authors rely on the
timestamp to judge whether the code has been copied from/to Stack Overflow along
with confirmations from six developers. Instead of Android apps, we investigated
clones between Stack Overflow and 111 open source projects. Their results are
similar to our findings that there exist clones from software projects to Stack
Overflow with potential licensing violations. Abdalkareem et
al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
android apps from F-Droid repository and used timestamp to determine direction
of copying. They found 22 apps containing code cloned from Stack Overflow. They
reported that cloned code are commonly used for enhancing existing code. Their
analysis shows that the cloned code from Stack Overflow have negative effects to
quality of the apps. The median percentage of bug fixing commits after adding
Stack Overflow code (19.09\%) is higher than before adding the code (5.96\%)
with statistical significance.
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
